Citeopotamus

### 2012-12-08 paper/paper.tex
Fixed some spelling.

\section{Introduction}\label{sec:introduction}
The problem of recommending citations for a technical paper is known and has
many approaches to attempt to solve it~\cite{cite1, cite2, cite3, cite4, cite5,
cite6, cite7, cite8}. Solutions range from graph based social network
approaches to language models to match meaning in both the paper and the
recommended text. But the problem of recommending where inside the paper to put
citations is unknown.  The ideal solution would recommend an exact spot in the
paper to put a specific citation. To solve this problem there exist two
separate pieces. First, given a location of a citation the solution must be
able to examine the references for the paper and choose the most appropriate
citations.  Second, find locations where citations should go. We leave the
second problem to be done in the future while we focus on solving the first in
this paper.

This paper discusses our approach to this problem, as well as the dataset we
procured for this use. In section \ref{sec:dataset} we highlight our dataset,
where it came from and what it contains. Section \ref{sec:architecture} follows
up with how we designed the system, our method of collecting our dataset, and
how it is structured, while section \ref{sec:parsing} goes into detail of how
our system parses and understands the publication text. Section
\ref{sec:methods} describes our methods for predicting a citation and section
\ref{sec:eval} discusses our approach for evaluating our system. Our results
are shown in section \ref{sec:results}, section \ref{sec:future} is where we
talk about future work and we discuss related work in section
\ref{sec:related}. Finally, we conclude our work in section
\ref{sec:conclusion}.

@@

Unfortunately, there was a problem as we were writing the information for some
of these reference papers to disk. In some cases the directory containing information for a
reference paper is incorrectly labelled. Specifically, as with the example
above, if we have a reference paper ``foo'' that is the fourth citation, our
dataset, as is, may have ``foo'' in a directory ``5.'' That is, instead of
``[4]'' being in the directory ``4,'' it is in the directory ``5.'' While this
is unfortunate, and can be redone (the raw HTML for every root paper has
information that would allow the reference directories to be properly renamed),
it could not be fixed at the time of getting results. So the results mentioned
in this paper reflect appropriate measures taken during the parsing phase,
further described in section \ref{sec:parsing}.

Every directory that represents a paper will have at most four files:
\begin{itemize}
   \item \textbf{meta.txt}\footnotemark[1]{} -- Contains the title, authors,
                                                tags, categories, and abstract.
                                                This is the only file required
                                                for every paper directory.
   \item \textbf{paper.txt}\footnotemark[1]{} -- The text version of the paper.
                                                 This file is required for the
                                                 root paper.
   \item \textbf{refs.txt}\footnotemark[1]{} -- Only the references that appear
                                                at the bottom of the paper.
                                                This information is duplicated
                                                in paper.txt, but placed here
                                                for convenience.
   \item \textbf{paper.pdf} -- The pdf version of the paper.
   \item \textbf{paper.html} -- The HTML version of the publication. This is
                                grabbed should the paper need to be re-parsed.
\end{itemize}

@@

\subsection{Citer}\label{sec:archCiter}
The citer begins by attempting to parse a directory structure into a structured collection of papers.
The citer then pre-processed each paper and generates a set of contexts (see Section \ref{sec:context}) for each citation in each
root paper.

After all of the contexts are generated, those contexts are fed into the Method Pipeline. In this pipeline are all the methods (see Section \ref{sec:methods})
that operate on the contexts to try and generate citations. Each citation in put through each method one at a time. If any method emits a value, then the pipeline
it short circuited and the emitted value is used as the citation. Because of this short circuiting behavior, the methods in the pipeline are ordered by approximate
precision. That is, all of the methods that rarely miss (regardless of how many citations they correctly place) are moved to the front of the pipeline.
As a citation travels through the pipeline, its citation becomes more and more uncertain.

@@

\subsection{OCR}
Before any parsing can be done a paper, it must first be converted to a plain text (UTF-8) format.
Since PLOS provides most of their papers in an HTML format, this only had to be done off-line for a few
papers. After looking at many alternatives, we chose to use ABBYY Finereader 10\cite{abbyy}. This
is a commercial OCR product, and requires a licence to use.

@@

\subsubsection{Ranges}
It is very common for authors to cite entire ranges at a time: $$[1] - [3]$$
This is especially seen when an author is referencing background material. These ranges must be expanded out to
the fill list of citations: $$[1][2][3]$$

\subsubsection{False Positive Sentence Enders}\label{sec:fpEnders}
Being able to split up paragraphs into sentences is very important to the Citeopotamus system.
We first tried to use NLTK's \textit{PunktSentenceTokenizer}. However, this did not seem to work well.
It seemed to have a problem with some of the symbols used in academic papers, such as the square brackets around
citations. To combat the punctuation tokenizing problem, we decided to only split sentence on periods, question marks, and
exclamations points. Additionally, we replaced common false positive sentence enters i.e.
$$i.e. => \_ie\_$$
$$dr. => \_dr\_$$
$$0.05 => \_0\_05\_$$

@@

\subsubsection{Sentence}
Sentence level contexts contain just the sentence that the citation was main in. As discussed in Section \ref{sec:fpEnders},
sentence context is parsed just by splitting the paragraph on sentence ending punctuation after false positives have been replaced.

@@

Using synonym can also help finding important words.

@@

\section{Related Work}\label{sec:related}
We were unable to find any related work on recommending citations given a spot for a citation to go. Unlike the problem of recommending citations for a paper. Copious amounts of work already exists on the topic. With several different approaches. One of the most common was using models to compare a paper and the rest of the dataset. Some of the models used includes translation models, probabilistic models, and several forms of LDAs.\cite{cite1, cite2, cite3} The next most common group of solutions was to use citations graphs to recommend missing citations.\cite{cite6} One group extended the notion of graphs and included metadata to help filter out results.\cite{cite4} One of the most 
interesting and unique approaches was to not look at co-citations but to look at co-accesses via logs like HTTP access records.\cite{cite7}
Another interesting approach used collaborative filtering to let communities help decide citations.\cite{cite8} For more related work in
citation recommendation we recommend the survey by McNee et al. they go into a lot of depth on the problem and common pitfalls.\cite{cite5}

@@

\section{Thanks}
We thanks the folks at PLOS for providing the source of our dataset. Without them this would of been a lot harder.

>>>>

\section{Introduction}\label{sec:introduction}
The problem of recommending citations for a technical paper is known and has
many approaches to attempt to solve it~\cite{cite1, cite2, cite3, cite4, cite5,
cite6, cite7, cite8}. Solutions range from graph based social network
approaches to language models that match meaning in both the paper and the
recommended text. On the other hand the problem of recommending where inside the paper to put
citations is unknown. The ideal solution would recommend an exact spot in the
paper to put a specific citation. To solve this problem there exist two
separate pieces. First, given a location of a citation the solution must be
able to examine the references for the paper and choose the most appropriate
citations. Second, find locations where citations should go. We leave the
second problem to be done in the future while we focus on solving the first in
this paper.

This paper discusses our approach to this problem, as well as the dataset we
procured for testing and future work on this problem..
In section \ref{sec:dataset} we highlight our dataset,
where it came from and what it contains. Section \ref{sec:architecture} follows
up with how we designed the system, our method of collecting our dataset, and
how it is structured, while section \ref{sec:parsing} goes into detail of how
our system parses and understands the publication text. Section
\ref{sec:methods} describes our methods for predicting a citation and section
\ref{sec:eval} discusses our approach for evaluating our system. Our results
are shown in section \ref{sec:results}, section \ref{sec:future} is where we
talk about future work and we discuss related work in section
\ref{sec:related}. Finally, we conclude our work in section
\ref{sec:conclusion}.

@@

Every directory that represents a paper will have at most five files:
\begin{itemize}
   \item \textbf{meta.txt}\footnotemark[1]{} -- Contains the title, authors,
                                                tags, categories, and abstract.
                                                This is the only file required
                                                for every paper directory.
   \item \textbf{paper.txt}\footnotemark[1]{} -- The text version of the paper.
                                                 This file is required for the
                                                 root paper.
   \item \textbf{refs.txt}\footnotemark[1]{} -- Only the references that appear
                                                at the bottom of the paper.
                                                This information is duplicated
                                                in paper.txt, but placed here
                                                for convenience.
   \item \textbf{paper.pdf} -- The pdf version of the paper.
   \item \textbf{paper.html} -- The HTML version of the publication. This is
                                grabbed should the paper need to be re-parsed.
\end{itemize}

@@

\subsection{Citer}\label{sec:archCiter}
The citer begins by attempting to parse a directory structure into a structured collection of papers.
The citer then pre-processes each paper and generates a set of contexts (see Section \ref{sec:context}) for each citation in each
root paper.

After all of the contexts are generated, those contexts are fed into the Method Pipeline. In this pipeline are all the methods (see Section \ref{sec:methods})
that operate on the contexts to try and generate citations. Each citation in put through each method one at a time. If any method emits a value, then the pipeline
is short circuited and the emitted value is used as the citation. Because of this short circuiting behavior, the methods in the pipeline are ordered by approximate
precision. That is, all of the methods that rarely miss (regardless of how many citations they correctly place) are moved to the front of the pipeline.
As a citation travels through the pipeline, its citation becomes more and more uncertain.

@@

\subsection{OCR}
Before any parsing can be done on a paper, it must first be converted to a plain text (UTF-8) format.
Since PLOS provides most of their papers in an HTML format, this only had to be done off-line for a few
papers. After looking at many alternatives, we chose to use ABBYY Finereader 10\cite{abbyy}. This
is a commercial OCR product, and requires a licence to use.

@@

\subsubsection{Ranges}
It is very common for authors to cite entire ranges at a time: $$[1] - [3]$$
This is especially seen when an author is referencing background material. These ranges must be expanded out to
the full list of citations: $$[1][2][3]$$

\subsubsection{False Positive Sentence Enders}\label{sec:fpEnders}
Being able to split up paragraphs into sentences is very important to the Citeopotamus system.
We first tried to use NLTK's \textit{PunktSentenceTokenizer}. However, this did not seem to work well.
It seemed to have a problem with some of the symbols used in academic papers, such as the square brackets around
citations. To combat the punctuation tokenizing problem, we decided to only split sentence on periods, question marks, and
exclamations points. Additionally, we replaced common false positive sentence enders i.e.
$$i.e. => \_ie\_$$
$$dr. => \_dr\_$$
$$0.05 => \_0\_05\_$$

@@

\subsubsection{Sentence}
Sentence level contexts contain just the sentence that the citation was made in. As discussed in Section \ref{sec:fpEnders},
sentence context is parsed just by splitting the paragraph on sentence ending punctuation after false positives have been replaced.

@@

Using synonyms could also help finding important words.

@@

\section{Related Work}\label{sec:related}
We were unable to find any related work on recommending citations given a spot for a citation to go.
Unlike the problem of recommending citations for a paper. Copious amounts of work already exists on the topic.
With several different approaches. One of the most common was using models to compare a paper and the rest
of the dataset. Some of the models used included translation models, probabilistic models, and several
forms of LDAs.\cite{cite1, cite2, cite3} The next most common group of solutions was to use citations
graphs to recommend missing citations.\cite{cite6} One group extended the notion of graphs and included metadata to help filter out results.\cite{cite4} One of the most 
interesting and unique approaches was to not look at co-citations but to look at co-accesses via logs like HTTP access records.\cite{cite7}
Another interesting approach used collaborative filtering to let communities help decide citations.\cite{cite8} For more related work in
citation recommendation we recommend the survey by McNee et al. because they go into a lot of depth on the problem and common pitfalls.\cite{cite5}

@@

\section{Thanks}
We thank the folks at PLOS for providing the source of our dataset. Without them this would of been a lot harder.
